Hello Window!

### 2011-05-08 article_intro_devel_content.tex
Standardized compilation commands.

\begin{lstlisting}[language=sh, numbers=none, basicstyle=\ttfamily, keywordsprefix=window, keywordstyle=\itshape, basewidth={0.5em, 0.4em}]
gcc gtk_window.c -o gtk_binary `pkg-config --cflags --libs gtk+-2.0`
g++ gtkmm_window.cc -o gtkmm_binary `pkg-config --cflags --libs gtkmm-2.4`
\end{lstlisting}

>>>>

\lstcompiles
{gtk\_sourcefile.c}{gtk\_binary}
{gtkmm\_sourcefile.cc}{gtkmm\_binary}

### 2011-05-08 article_window_content.tex
Standardized compilation commands.

\begin{lstlisting}[language=bash, numbers=none, basicstyle=\ttfamily, keywordsprefix=window, keywordstyle=\itshape, basewidth={0.5em, 0.4em}]
gcc gtk_source_file.c -o gtk_binary `pkg-config --cflags --libs gtk+-2.0`
g++ gtkmm_source_file.cc -o gtkmm_binary `pkg-config --cflags --libs gtkmm-2.4`
\end{lstlisting}

>>>>

\lstcompiles
{gtk_sourcefile.c}{gtk_binary}
{gtkmm_sourcefile.cc}{gtkmm_binary}
